---
title: "Reporting Demo"
author: "Tom Watson"
date: Today
output:
  html_document:
    theme: united
---

This is a demo document for the reporting project using the demo campaign.
Its basically a scratch pad for themes, layouts and types of graphs while we refine what we want to send to clients (and what clients think they want :P )
Please note, graph asethetics are not finalised-things like colours, minor layout details, labels, column values, etc will be added in/finalised later.

```{r, echo = FALSE, collapse = TRUE, warning= FALSE, message= FALSE, include= FALSE, CairoPlot}
BaseData = read.csv(file = 'Base.csv', header = TRUE, sep = ,) # Base Data contains everything about campaign except hour and custom report information
require(ggplot2)
require(dplyr)
require(lubridate) #Because dplyr doesn't support dates unless they're POSIXCT format
require(Cairo) #For anti aliasing graphs
require(grid)
require(ggthemes)
FlatUI = c(Turquoise = "#1abc9c", # FlatUI colour palette for nicer, material design appearance
            Greensea = "#16a085",
            Emerald = "#2ecc71",
            Nephritis = "#27ae60",
            PeterRiver = "#3498db",
            BelizeHole = "#2980b9",
            Amethyst = "#9b59b6",
            Wisteria = "#8e44ad",
            WetAsphalt = "#34495e",
            MidnightBlue = "#2c3e50",
            SunFlower = "#f1c40f",
            Orange = "#f39c12",
            Carrot = "#e67e22",
            Pumpkin = "#d35400",
            Alizarin = "#e74c3c",
            Pomegranate = "#c0392b",
            Clouds = "#ecf0f1",
            Silver = "#bdc3c7",
            Concrete = "#95a5a6",
            Asbestos = "#7f8c8d")

BaseData = BaseData[1:(dim(BaseData)[1]-1),] # Remove the last line containing the totals.
BaseData$Impressions = gsub(",","", BaseData$Impressions, fixed = TRUE) # Remove the comma's from the values
BaseData$Clicks = gsub(",","", BaseData$Clicks, fixed = TRUE)
BaseData$Impressions = as.numeric(BaseData$Impressions)
BaseData$Clicks = as.numeric(BaseData$Clicks)
BaseData$Date = mdy(BaseData$Date)
ToDrop = c("CTR", "Fill.Rate", "Conversions", "eCPM", "Revenue", "IAB.Tier.1.Categories")
BaseData = BaseData[, !(names(BaseData) %in% ToDrop)] # Drop variables useless for external reporting
PlotData = aggregate(cbind(BaseData$Impressions, BaseData$Clicks) ~ BaseData$Date, BaseData, FUN = sum)
colnames(PlotData) = c("Date", "Impressions", "Clicks") #Rename to more readable formats

PlotData$CTR = (PlotData$Clicks/PlotData$Impressions)
PlotData$CumlCTR = (cumsum(PlotData$Clicks))/(cumsum(PlotData$Impressions))
BasePlot = ggplot(PlotData, aes(Date, Impressions, Clicks, CTR))

ImpDatePlot = BasePlot + # Impressions by date plot
  geom_path(aes(y = Impressions), size = 0.5, colour = FlatUI["BelizeHole"]) +
  labs(title = "Impressions per day", x = "Date", y = "Impressions") +
  scale_y_continuous(breaks = c(0,10000,20000,30000,40000,50000,60000,70000)) +
  theme_few() +
  theme(plot.title = element_text(size = 16, family = "Ubuntu"),
        text = element_text(family = "Ubuntu Light"),
        plot.margin = unit(c(0,0,2,0),"cm"),
        panel.border = element_blank())

ImpCumSumPlot = BasePlot + # Cumulative impressions by date
  geom_path(aes(y = cumsum(PlotData$Impressions))) +
  geom_area(aes(y=cumsum(PlotData$Impressions)), fill = "#009BDC", alpha = 0.5) +
  scale_y_continuous(breaks = round(seq(0,max(cumsum(PlotData$Impressions)), length.out = 10))) +
  labs(title = "Cumulative Impressions by date", x = "Date", y = "") +
  theme_few() +
  scale_colour_few() +
  theme(plot.title = element_text(size = 16, family = "Ubuntu"),
        text = element_text(family = "Ubuntu Light"),
        plot.margin = unit(c(0,0,2,0),"cm"),
        panel.border = element_blank())

ClickDatePlot = BasePlot + # Clicks by date plot
  geom_path(aes(y = Clicks), colour = "#009BDC", size = 0.4) +
  labs(title = "Clicks per day", x= "Date", y = "Clicks") +
  scale_y_continuous(breaks = seq(0, max(PlotData$Clicks), by = 50)) +
  theme_few() +
  scale_colour_few() +
  theme(plot.title = element_text(size = 16, family = "Ubuntu"),
        text = element_text(family = "Ubuntu Light"),
        plot.margin = unit(c(0,0,2,0), "cm"),
        panel.border = element_blank())

ClickCumSumPlot = BasePlot + # Cumulative clicks by date
  geom_path(aes(y = cumsum(PlotData$Clicks))) +
  geom_area(aes(y=cumsum(PlotData$Clicks)), fill = "#009BDC", alpha = 0.5) +
  scale_y_continuous(breaks = round(seq(0,max(cumsum(PlotData$Clicks)), length.out = 10))) +
  labs(title = "Cumulative Clicks by date", x = "Date", y = "Cumulative Clicks") +
  theme_few() +
  scale_colour_few() +
  theme(plot.title = element_text(size = 16, family = "Ubuntu"),
        text = element_text(family = "Ubuntu Light"),
        plot.margin = unit(c(0,0,2,0), "cm"),
        panel.border = element_blank())

CTRDatePlot = BasePlot + # CTR (click through rate) by date
  geom_path(aes(y = CTR), colour = "#009BDC", size = 0.4) +
  labs(title = "CTR per day", x = "Date", y = "CTR") +
  scale_y_continuous(breaks = seq(0,max(PlotData$CTR), length.out = 10), labels = scales::percent) +
  theme(plot.margin = unit(c(0,0,2,0),"cm")) +
  theme_few() +
  scale_colour_few() +
  theme(plot.title = element_text(size = 16, family = "Ubuntu"),
        text = element_text(family = "Ubuntu Light"),
        plot.margin = unit(c(0,0,2,0),"cm"),
        panel.border = element_blank())

CTRCumlPlot = BasePlot + # Total CTR by date/cumulative CTR
  geom_path(aes(y = CumlCTR)) +
  geom_area(aes(y=CumlCTR), fill = "#009BDC", alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, max(PlotData$CumlCTR), length.out = 10), labels = scales::percent) +
  labs(title = "Cumulative CTR", x = "Date", y = "CTR") +
  theme_few() +
  scale_colour_few() +
  theme(plot.title = element_text(size = 16, family = "Ubuntu"),
        text = element_text(family = "Ubuntu Light"),
        plot.margin = unit(c(0,0,2,0), "cm"),
        panel.border = element_blank())

CreativeData = aggregate(cbind(BaseData$Impressions, BaseData$Clicks, BaseData$Banners) ~ BaseData$Date + BaseData$Banners, FUN = sum)
CreativeData$V3 = NULL
colnames(CreativeData) = c("Date", "Banner", "Impressions", "Clicks")

BaseCreativePlot =  ggplot(CreativeData, aes(Date, Impressions, Clicks)) # Creative impression plot
CreativeImpressionPlot = BaseCreativePlot +
  geom_area(aes(y = Impressions, colour = Banner, fill = Banner), position = 'stack') + # stacked to give an indication of what percentage of delivery
  theme_few() + # each creative accounts for
  scale_colour_few() +
    labs(title = "Impressions per day by creative", x = "Date", y = "Impressions") +
  theme(panel.grid = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank(),
        plot.title = element_text(size = 16, family = "Ubuntu"),
        text = element_text(family = "Ubuntu Light") ,
        plot.margin = unit(c(0,0,2,0), "cm"))

CreativeClickPlot = BaseCreativePlot + # Creative Click plot
  geom_area(aes(y = Clicks, colour = Banner, fill = Banner), position = 'stack') +
  theme_few() +
  scale_colour_few() +
  labs(title = "Clicks per day by Creative", x = "Date", y = "Clicks") +
  theme(panel.grid = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank(),
        plot.title = element_text(size = 16, family = "Ubuntu"),
        text = element_text(family = "Ubuntu Light"),
        plot.margin = unit(c(0,0,2,0),"cm"))

rm(BaseData)
rm(CreativeData)

StrTemp = readLines("Hour.csv") # If you get an error here, put a newline character at the end of the file
HourData = read.csv(text = StrTemp, skip = 4, nrow = length(StrTemp) -6, header= TRUE, sep = ",")
HourData = subset(HourData, select = c(Hour, Impressions, Clicks))
HourData$Hour = as.numeric(HourData$Hour)
for(i in seq(1, length(HourData$Hour), by =1)){
  HourData$Hour[i] = (i + 10) %% 24
}
HourData = HourData[order(HourData$Hour),]
row.names(HourData) = NULL
HourData$CTR = HourData$Clicks/HourData$Impressions
HourData$CTR = HourData$CTR*100
HourData$dummy = 0

CTRHeat = ggplot(HourData,aes(x = dummy, y = Hour,)) +
  geom_tile(aes(fill = CTR)) +
  scale_fill_gradient(low = "white", high = FlatUI["Pumpkin"]) +
  labs(x = NULL) +
  xlim(c(-0.6,0.6)) +
  scale_y_continuous(breaks = seq(0,23, by = 2)) +
  coord_flip() +
  theme_few() +
  scale_colour_few() +
  labs(title = "CTR by Hour (24 Hour format)") +
  theme(panel.background = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        plot.title = element_text(size = 16, family = "Ubuntu"),
        text = element_text(family = "Ubuntu Light"),
        plot.margin = unit(c(0,0,2,0), "cm"),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())
# Super neat heatmap style plot for CTR


CustomData = read.csv("Custom.csv", header = TRUE, sep = ",") # Read in custom data csv
CustomData = subset(CustomData, select = c(Device.OS, Geo.Region, Device.Type, Impressions, Clicks)) # A neater way to select the data we actually want
colnames(CustomData) = c("OS", "State", "Type", "Impressions", "Clicks") # Rename things to more useable names
CustomData$OS = gsub("[\\d-.]*", "", CustomData$OS, perl = TRUE) # Remove version numbers
CustomData$OS = gsub("Android.+", "Android", CustomData$OS) # Clean 'Android....' entries
CustomData$OS = gsub("iPhone OS", "iOS", CustomData$OS) # Clean 'iPhone/iOS/etc...' entries
CustomData$OS = gsub("^(?!.*(Android|iOS)).*", "Other", CustomData$OS, ignore.case = FALSE, perl = TRUE) # Label everything that's not Android or iOS as 'Other'

# Regex code for finding Android strings: /Android[\d-.]*/g
# Regex code for finding iOS strings: /iPhone OS[\d-.]*/g

OStemp = aggregate(cbind(CustomData$Impressions, CustomData$Clicks) ~ CustomData$OS, FUN = sum) # Aggregate on OS for graphs
colnames(OStemp) = c("OS", "Impressions", "Clicks")
OStemp$ImpFrac = OStemp$Impressions/sum(OStemp$Impressions) # generate values for percentage of total impressions
OStemp$ClickFrac = OStemp$Clicks/sum(OStemp$Clicks)
OStemp$ImpMax = cumsum(OStemp$ImpFrac)
OStemp$ClickMax = cumsum(OStemp$ClickFrac)
OStemp$ImpMin = c(0, head(OStemp$ImpMax, n = -1))
OStemp$ClickMin = c(0, head(OStemp$ClickMax, n = -1))

OSData = ggplot(OStemp, aes(fill = OS)) +
 geom_rect(aes(ymax = ImpMax, ymin = ImpMin, xmax = 0.6, xmin = 0.3), colour = "white") + #position the rectangles
 geom_rect(aes(ymax = ClickMax, ymin = ClickMin, xmax = 0.3, xmin = 0), colour = "white") +
 labs(x= NULL, y = NULL) +
 geom_text(aes(label = paste(round(ImpFrac*100, 2), "%"), x = 0.45, y = ((ImpMax + ImpMin)/2), inherit.aes = TRUE, show.legend = FALSE), family = "Ubuntu Light") + #position the % values
 geom_text(aes(label = paste(round(ClickFrac*100,2),"%"), x = 0.15, y = ((ClickMin + ClickMax)/2), inherit.aes = TRUE, show.legend = FALSE), family = "Ubuntu Light") +
 coord_flip() +
 theme_few() +
 scale_colour_few() +
 xlim(-0.1,0.7) +
 ylim(-0.2,1) +
 theme(panel.grid = element_blank(),
       axis.text = element_blank(),
       axis.ticks = element_blank(),
       panel.background = element_blank(),
       legend.position = "bottom",
       legend.title = element_blank(),
       plot.margin = unit(c(0,0,2,0), "cm"),
       panel.border = element_blank(),
       legend.position = "bottom") +
 annotate("text", # position the labels
          x = 0.45,
          y = -0.105,
          label = "Impressions",
          size = 5,
          family = "Ubuntu Light") +
 annotate("text",
          x = 0.15,
          y = -0.05,
          label = "Clicks",
          size = 5,
          family = "Ubuntu Light") +
 annotate("text",
          x = 0.7,
          y = 0.5,
          label = "Platform Breakdown",
          size = 6,
          family = "Ubuntu Light")

Statetemp = aggregate(cbind(CustomData$Impressions, CustomData$Clicks) ~ CustomData$State, FUN = sum)
colnames(Statetemp) = c("State", "Impressions", "Clicks")
Statetemp = Statetemp[!(Statetemp$State == ""),]
row.names(Statetemp) = NULL
Statetemp$ImpFrac = Statetemp$Impressions/sum(Statetemp$Impressions)
Statetemp$ClickFrac = Statetemp$Clicks/sum(Statetemp$Clicks)
Statetemp$ImpMax = cumsum(Statetemp$ImpFrac)
Statetemp$ClickMax = cumsum(Statetemp$ClickFrac)
Statetemp$ImpMin = c(0, head(Statetemp$ImpMax, n = -1))
Statetemp$ClickMin = c(0, head(Statetemp$ClickMax, n = -1))

Stateplot = ggplot(Statetemp, aes(fill = State)) +
  geom_rect(aes(ymin = ImpMin, ymax = ImpMax, xmin = 0.2, xmax = 0.4), colour = "White") +
  geom_rect(aes(ymin = ClickMin, ymax = ClickMax, xmin = 0, xmax = 0.2), colour = "white") +
  xlim(c(-0.1,0.5)) +
  ylim(c(-0.2,1)) +
  annotate("text",
           x = 0.3,
           y = -0.14,
           label = "Impressions",
           size = 5,
           family = "Ubuntu Light") +
  annotate("text",
           x = 0.1,
           y = -0.09,
           label = "Clicks",
           size = 5,
           family = "Ubuntu Light") +
  annotate("text",
           x = 0.5,
           y = 0.5,
           label = "State Breakdown",
           size = 6,
           family = "Ubuntu Light") +
  geom_text(aes(label = paste(round(ImpFrac*100,2), "%"), x = 0.3, y = ((ImpMax + ImpMin)/2), inherit.aes = TRUE, show.legend = FALSE), # puts the label in the middle of the bar
                angle = 45, # Angle in degrees
                family = "Ubuntu") +
  geom_text(aes(label = paste(round(ClickFrac*100,2), "%"), x = 0.1, y = ((ClickMax + ClickMin)/2),
                angle = 45,
                inherit.aes = TRUE,
                show.legend = FALSE),
                family = "Ubuntu") +
  labs(x = NULL, y = NULL) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank(),
        panel.background = element_blank(),
        legend.title = element_blank(),
        legend.position = "bottom",
        legend.key = element_rect(colour = "white"),
        plot.margin = unit(c(0,0,2,0),"cm")) +
  coord_flip()
plot(Stateplot)
```

```{r, echo = FALSE, collapse = TRUE, warning= FALSE, message= FALSE, fig.show='hold', fig.width=4.7, fig.asp=1, dev='CairoPNG'}
ImpDatePlot
ImpCumSumPlot
# rm(ImpDatePlot)
# rm(ImpCumSumPlot)
```
```{r, echo = FALSE, collapse = TRUE, warning= FALSE, message= FALSE, fig.show='hold', fig.width=4.7, fig.asp=1, dev='CairoPNG'}
ClickDatePlot
ClickCumSumPlot
# rm(ClickDatePlot)
# rm(ClickCumSumPlot)
```
```{r, echo = FALSE, collapse = TRUE, warning= FALSE, message= FALSE, fig.show='hold', fig.width=4.7, fig.asp=1, dev='CairoPNG'}
CreativeImpressionPlot
CreativeClickPlot
```
```{r, echo = FALSE, collapse = TRUE, warning= FALSE, message= FALSE, fig.show='hold', fig.width=4.7, fig.asp=1, dev='CairoPNG'}
CTRDatePlot
CTRCumlPlot
```
```{r, echo = FALSE, collapse = TRUE, warning= FALSE, message= FALSE, fig.show='hold', fig.asp=0.5, fig.align='center', dev='CairoPNG'}
CTRHeat
```
```{r, echo = FALSE, collapse = TRUE, warning= FALSE, message= FALSE, fig.show='hold', fig.asp=0.5, fig.align='center', dev='CairoPNG'}
OSData
```

```{r, echo = FALSE, collapse = TRUE, warning= FALSE, message= FALSE, fig.show='hold', fig.asp=0.5, fig.align='center', dev='CairoPNG'}
Stateplot
```
